Discrete Quantum Theories and Computing

### 2018-04-15 dissertation.tex
prop.bib @Misc{THOS2017} updated to eliminating the version...

\begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2018}
with me, and enormous other things. These papers become the main part
of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2018}.
Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
you for getting together to understand what I did and passing my dissertation
proposal Spring 2017. Also, thank Prof. Dylan Thurston for serving
in my advisory committee and my Tier 3 committee, with other advisory
committee members passing my Computer Science qualifying exam Spring
2016. Especially, my survey of real computation in the qualifying
exam inspires me the comparison of quantum computer and analog computer
in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
also contains the motivation in my application for Rethinking Foundations
of Physics 2017 workshop reviewed by Prof. Amr Sabry. Thank Prof.
Lawrence Moss for inviting me to present our results in the interdisciplinary
logic seminar and SICE theory seminar, co-chairing my Tier 3 committee,
writing an assessment letter for me, and drawing my attention on Prof.
Abramsky's paper~\cite{Abramsky2012}, which inspired me to merge
quantum probability with discrete quantum theories. Thank John Gardiner
for inspiring discussion on the difficulties merging them~\cite{Gardiner2014}.
These results are improved and motivated the transition from DQT to
QIVPM in Sec.~\ref{sec:Toward-IVPM}. Thank Prof. Tom Lewis for helping
me organize the unpublished deterministic quantum algorithms in the
term paper for SLST-T501 Academic Writing course as presented in Sec.~\ref{discretequantumtheoryI}.
Thank Traci Nagle for going through the literature review about finite
precision measurement and contextuality discussed for CSCI-Y790 Writing
and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.

@@

\section{Quantum Contextuality\label{sec:Quantum-Contextuality}}

>>>>

\begin{acknowledgments}Thank Prof. Gerardo Ortiz, Prof. Amr Sabry,
and Prof. Andrew Hanson for publishing three papers \cite{geometry2013,DQT2014,THOS2017}
with me, and enormous other things. These papers become the main part
of my thesis, especially most of Chapter~\ref{chap:DQT=000026DQC}
is based on ``Geometry of discrete quantum computing''~\cite{geometry2013}
and ``Discrete quantum theories'' (DQT)~\cite{DQT2014}; most of
Chapter~\ref{chap:QIVPM} is based on ``Quantum Interval-Valued
Probability: Contextuality and the Born Rule'' (QIVPM) \cite{THOS2017}.
Together with Prof. Dylan Thurston and Prof. Shouhong Wang, thank
you for getting together to understand what I did and passing my dissertation
proposal Spring 2017. Also, thank Prof. Dylan Thurston for serving
in my advisory committee and my Tier 3 committee, with other advisory
committee members passing my Computer Science qualifying exam Spring
2016. Especially, my survey of real computation in the qualifying
exam inspires me the comparison of quantum computer and analog computer
in Chapter~\ref{chap:Introduction}. Chapter~\ref{chap:Introduction}
also contains the motivation in my application for Rethinking Foundations
of Physics 2017 workshop reviewed by Prof. Amr Sabry. Thank Prof.
Lawrence Moss for inviting me to present our results in the interdisciplinary
logic seminar and SICE theory seminar, co-chairing my Tier 3 committee,
writing an assessment letter for me, and drawing my attention on Prof.
Abramsky's paper~\cite{Abramsky2012}, which inspired me to merge
quantum probability with discrete quantum theories. Thank John Gardiner
for inspiring discussion on the difficulties merging them~\cite{Gardiner2014}.
These results are improved and motivated the transition from DQT to
QIVPM in Sec.~\ref{sec:Toward-IVPM}. Thank Prof. Tom Lewis for helping
me organize the unpublished deterministic quantum algorithms in the
term paper for SLST-T501 Academic Writing course as presented in Sec.~\ref{discretequantumtheoryI}.
Thank Traci Nagle for going through the literature review about finite
precision measurement and contextuality discussed for CSCI-Y790 Writing
and Editing course as presented in Sec.~\ref{sec:Quantum-Contextuality}.

@@

\section{Hidden Variable Model and Quantum Contextuality\label{sec:Quantum-Contextuality}}
